%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Professional CV
% LaTeX Template
% Version 2.0 (8/5/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Rishi Shah 
%
% Important note:
% This template requires the resume.cls file to be in the same directory as the
% .tex file. The resume.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.75in,top=0.6in,right=0.75in,bottom=0.6in]{geometry} % Document margins
\usepackage[colorlinks = true,
            linkcolor = blue,
            urlcolor  = blue,
            citecolor = blue,
            anchorcolor = blue]{hyperref}
\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}}
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}
\name{Ronak Shailesh Vyas} % Your name
\address{Senior Software Engineer at MiQ}
\address{BTech(CSE) NIT Goa \\ Java \\ Microservices \\ ReactJS \\ Vert.x \\ Spring \\ Design  \\ CI/CD}
\address{(+91)8140465737 \\ \href{mailto:ronaksvyas@gmail.com}{ronaksvyas@gmail.com}} % Your phone number and email

\begin{document}

%--------------------------------------------------------------------------------
%    Experience
%-----------------------------------------------------------------------------------------------
\begin{rSection}{Experience}
{\bf \href{http://wearemiq.com}{MiQ} \hfill{September 2016 - Present}}
\\MiQ is a Marketing Intelligence company which helps businesses grow through Data Driven Solutions.
\begin{itemize}
    
    \item {\bf{AiQx}} : AiQx is the Client Facing Discovery Platform of MiQ which enables Agencies to plan Campaigns and discover Insights.
    \begin{enumerate}
        \item Involved in designing and implementing UI and Backend Microservices from scratch. 
        \item Integrated Vert.x in the existing architecture at a later stage.
        \item Worked on design and implementation of Universal Search which involves Searching and Querying on hundreds of GBs of row level data and generating reports on it using Elastic Search, Amazon Athena, Vert.x, Memcached etc.
        \item Designed and implemented CSV Download of Reports.
        \item Mentored Engineers and Interns joining the team to get them familiarized with the Product, Processses and Tech Stack.
        \item Instrumental in improvement of CI/CD pipeline using Docker, Jenkins and Kubernetes.
        \item Implemented various Developer Productivity processes like Pull Request Guidelines, Coding Conventions etc.
        \item {\bf{Tech Stack}}: ReactJS, Java, Websockets, Apache Camel, Vert.x, Amazon Athena, MySQL, Jenkins, Docker, Kubernetes, Spring.
    \end{enumerate}
\end{itemize}}

\begin{itemize}
    \item {\bf{Jarvis}} : Jarvis is the backbone application of MiQ. It is a Campaign management system which helps Traders manage their Advertising Campaigns efficiently, saving their precious time. 
    \begin{enumerate}
        \item Implemented various types of Cost Tracking on Campaigns to help Finance team with their billing.
        \item Isolated highly coupled modules into independent Microservices.
        \item Designed a Generic DSP(Demand Side Platform) Microservice which will help us scale to multiple DSPs in future.
        \item Implemented best practices like Pull Request Guidelines, Release Process, Coding Guidelines etc. which resulted in increase in faster development and stability.
        \item Organized an one day Hackathon which resulted in us implementing a new Generic DSP Microservice.
        \item {\bf{Tech Stack}}: Vert.x, REST API using Vert.x, MongoDB
    \end{enumerate}
    \item {\bf{MiQ Explore}} : MiQ Explore is an Insights Discovery tool which helps people within the company share and discover insights easily, sparing them the rework.
    \begin{enumerate}
        \item Single handedly Designed and Implemented the complete backend of MiQ Explore. This project was not a part of Product Roadmap and was done to solve a major problem on Analysis side of business. Received appreciation from the Board for solving a daily problem without being asked.
        \item {\bf{Tech Stack}}: Vert.x, REST API using Vert.x, MongoDB
    \end{enumerate}
    \item {\bf{SRS}} : SRS is the most widely used reporting tool for generating reports based on dimensions and metrics by the Analytics team.
    \begin{enumerate}
        \item Worked on UI and Backend enhancements.
        \item Implemented streaming download from S3 to UI.
        \item {\bf{Tech Stack}}: ReactJS, Java, Spring, AWS SDK, MongoDB. 
    \end{enumerate}
\end{itemize}


{\bf \href{https://unbxd.com}{Unbxd} \hfill{February 2016 - August 2016}}
\\Unbxd is a leading e-commerce product discovery platform that applies advanced data sciences to connect shoppers to the products they are most likely to buy, while providing predictive actionable insights for merchandising.
\begin{itemize}
    \item Worked as a Software Engineer in the Customer Success team. Built configurable plugins for various e-commerce platforms smoothening the integration process.
    \item {\bf{Tech Stack}}: Python, Java, MySQL, Solr, ElasticSearch. 
\end{itemize}

{\bf \href{https://coupondunia.com}{CouponDunia } \hfill{June 2014 - February 2016}}
\\CouponDunia is India's #1 Coupon and Cashback Destination. 

\begin{itemize}
    \item Built a generic and scalable data tracking system using RabbitMQ, Yii2 RESTful API, Multithreaded Java workers and PostgreSQL.
\item Implemented the complete Search functionality using SOLR with Solarium. Used clustering to
predict similar queries and tuned SOLR for relevancy.
\item Worked on the development of a custom MVC framework for Web and Mobile APIs.
\item Implemented a cron execution and management system which includes monitoring, logging and
scheduling of crons.
\item Developed an admin panel for sending mobile push notifications through parse with
scheduling and segmentation.
\item Developed Mobile APIs using PHP.
\item Developed the SEO panel to manage various tags for SEO. Implemented a dynamic template
system for all tags.
\item Developed a small framework to facilitate the use of Google Analytics for tracking various events
in Javascript.
\item Implemented various Admin panel functionalities for the Content team
 \item {\bf{Tech Stack}}: PHP, RabbitMQ, Yii Framework, Java, MySQL, PostgreSQL
\end{itemize}
\\{\bf Indirect Model Analysis of Structures}\\
Presented a Seminar on Indirect Model Analysis, explaining the method to compute response of Prototype from the Influence lines obtained from Model. Use of Muller Breslau Principle in Indirect Model Analysis and the Similitude between prototype and  model.\\

\\{\bf Microtunneling}\\
Presented a seminar on Micro Tunneling, explaining its advantages over conventional method of drainage laying systems. Analysis considering direct and indirect cost of micro tunneling was also discussed.

\end{rSection}


%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------
\newpage
\begin{rSection}{Education}

{\bf National Institute of Technology, Goa} \hfill {\em August 2010 - May 2014} 
\\ Bachelor of Technology
\\ Computer Science & Engineering \hfill{CGPA: \bf{8.35}}\\
\\{\bf Kendriya Vidyalaya, Silvassa} 
\\ Class 10\hfill { 2007, 88\%}
\\ Class 12\hfill {2009, 90.6\%}


\end{rSection}
{All the information provided above is accurate to the best of my knowledge}

\end{document}

